\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-05-02 journalSwarmControl/relatedWork.tex
added cover letter and other edits to the paper (mean = std, previous work by author)

>>>>

\subsection{Relationship to authors' prior work}
 This paper combines the content of two preliminary conference papers, extending their substance and providing full details in a single journal paper.  One paper covered the first three months of SwarmControl.net experiments~\cite{swarmcontrol2013}, and the second presented simulations of object manipulation~\cite{ShahrokhiIROS2015}. This paper presents three years of results from SwarmControl.net. For object manipulation, this paper presents robust new algorithms for manipulation, path planning, and obstacle avoidance, and a rich set of parameter sweeps over key variables. All hardware validation experiments are new.

### 2017-05-02 journalSwarmControl/simulation.tex
Some of Dylan's comments are affected
added cover letter and other edits to the paper (mean = std, previous work by author)

Our simulations use a Javascript port of \href{http://box2d.org/}{Box2D}, a popular 2D physics engine with support for rigid-body dynamics and fixed-time step simulation, presented in \cite{catto2010box2d}.  All experiments ran on a Chrome web browser on a 2.6 GHz Macbook.  \href{https://github.com/aabecker/SwarmControlSandbox/blob/master/exampleControllers/BlockPushingIROS2015.html}{All code is available at}~\cite{Shahrokhi2016blocksimulations}.

\subsection{Controlling the mean position}

We performed a parameter sweep using the PD controller \eqref{eq:PDcontrolPosition} to identify the best control gains.  Representative experiments are shown in Fig.~\ref{fig:gainvalues}. 100 particles were used and the maximum speed was 3 meters per second. As shown in Fig.~\ref{fig:gainvalues}, we can achieve an overshoot of 1\% and a  rise time of 1.52~s with $K_{p}= 4$, and  $K_{d} = 1$. 
\begin{figure}
\centering
\begin{overpic}[width = \columnwidth ]{gains.pdf}
\end{overpic}
%\begin{overpic}[width =0.49\columnwidth]{meanVariance4.eps} 
%\end{overpic} 
\vspace{-1em} 
\caption{\label{fig:gainvalues} In simulation, tuning proportional ($K_p$, top) and derivative ($K_d$, bottom)  gain values in \eqref{eq:PDcontrolPosition} improves performance with $n = 100$ particles. %b) Simulation result with 100 robots under hybrid control Alg.~\ref{alg:MeanVarianceControl}, which  controls both the mean position (top) and variance (bottom). For ease of analysis, only $x$ position and variance are shown.
%\vspace{-2em}
}
\end{figure}

>>>>

Our simulations use a Javascript port of \href{http://box2d.org/}{Box2D}, a popular 2D physics engine with support for rigid-body dynamics and fixed-time step simulation, presented in \cite{catto2010box2d}.  All experiments in this section ran on a Chrome web browser on a 2.6 GHz Macbook.  \href{https://github.com/aabecker/SwarmControlSandbox/blob/master/exampleControllers/BlockPushingIROS2015.html}{All code is available at}~\cite{Shahrokhi2016blocksimulations}.

\subsection{Controlling the mean position}
\begin{figure}
\centering
\begin{overpic}[width = \columnwidth ]{gains.pdf}
\end{overpic}
%\begin{overpic}[width =0.49\columnwidth]{meanVariance4.eps} 
%\end{overpic} 
\vspace{-1em} 
\caption{\label{fig:gainvalues} In simulation, tuning proportional ($K_p$, top) and derivative ($K_d$, bottom)  gain values in \eqref{eq:PDcontrolPosition} improves performance with $n = 100$ particles. %b) Simulation result with 100 robots under hybrid control Alg.~\ref{alg:MeanVarianceControl}, which  controls both the mean position (top) and variance (bottom). For ease of analysis, only $x$ position and variance are shown.
%\vspace{-2em}
}
\end{figure}
We performed a parameter sweep using the PD controller \eqref{eq:PDcontrolPosition} to identify the best control gains.  Representative experiments are shown in Fig.~\ref{fig:gainvalues}. 100 particles were used and the maximum speed was 3 meters per second. As shown in Fig.~\ref{fig:gainvalues}, we can achieve an overshoot of 1\% and a  rise time of 1.52~s with $K_{p}= 4$, and  $K_{d} = 1$.
